\chapter{Future Work}
\label{chap:todo}
After the investigation of Kinect's capabilities in order to achieve the requirements of Project Recon, a number of projects could be taken up, especially involving the new Kinect for XBox One.

After the limitations described, future work should focus on tackling them with different approaches. Creating a more reliable way to recognize gestures and moves other than IR (infrared rays) as interference is possible if there are other devices around emitting IR. Other recommendation is to use multiple 3D cameras in a room to be able to create an acurate model of the user and understand his motion.

Kinect for XBox One is a great approach as well. As it has increased the number of joints that are recognized from the user by the Kinect. Adding joints like the thumb and more. This will help in having accurate distinctions between moves. Taking the example of the punch technique from the conclusion section, the new Kinect will be sensitive enough to recognize these minor moves of the palm facing downwards or upwards since now the thumb is a joint that will be recognized.

The new XBox One Kinect has a wide-angle and bigger range than the older Kinect. Also the IR sensor and emitter are now updated and work with what is known as time-of-flight camera, unlike the VGA that was used in the older Kinect. The newer Kinect has better accuracy than the older one as it has a higher capture rate and an HD camera. Another addition is that the new Kinect is able to perform heart rate tracking. Heart rate tracking is one of the requirements for Project Impact.